Redshift evolution of the SN stretch distribution

### 2019-10-18 Nicolas.tex
Updated plots from variaIa update

@@

To determine this limit, we first took the observed counts in each bin of the
histograms. We then fitted $a$ on these counts for different numbers of bins
used to fit: the quality of the fit diminishes when we use bins that include
selection effects. To quantize this, we computed the expected counts from the
fitted $a$ in the same bins we used for the observed counts. That allowed us to
compute the poissonian probability in each bin, given by
\begin{center}
    $ \displaystyle p(k) = \frac{\lambda^k}{k!}e^{-\lambda}$
\end{center}
with $k$ the expected counts, $\lambda$ the observed counts. This work is done 100
times with a random number of total bins, $a$ being fitted 4 times on a
different and random number of bins used to fit each time. We interpolate these
400 poissonian evolutions to get one final result that is as close as possible
to accurately represent how the probability to follow the expected rate evolves.

@@

\begin{table}[htbp!]
    \centering
    \caption{Number of SNe Ia effectively used for each survey.}
    \label{tab:sample}
    \begin{tabularx}{\linewidth}{|Y*{1}{|Y}|}\hline
        \rowcolor{gray!15} Survey & Number of SNe Ia \\\hline\hline
        SNf & 141 \\\hline
        PS1 & 178 \\\hline
        SDSS & 206 \\\hline
        SNLS & 138 \\\hline
        HST & 26 \\\hline
    \end{tabularx}
\end{table}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=\linewidth]{Article_figures/zmax_determination.pdf}
    \caption{$z\St{max}$ determination from the interpolated poissonian
    evolutions.}
    \label{fig:zdet}
\end{figure}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=\linewidth]{Article_figures/surveys_cuts_x.pdf}
    \caption{SDSS, SNLS and PS1 samples cut at $z\St{max}$ as explained in
    section \ref{sec:sam}. The data we use is in plain markers.}
    \label{fig:surveys_cuts}
\end{figure}

\section{Method}
We used LsSFR measurments which evolution with the redshift is analytically
known (references) and stretch measurments made by SNf to try an correlate these
to parameters. We fit different model, and compare their AICc.

>>>>

\def\l{\lambda}\def\L{\Lambda}

@@

To determine this limit, we first took the observed counts in each bin of the
histograms. We then fitted $a$ on these counts for different numbers of bins
used to fit: the quality of the fit diminishes when we use bins that include
selection effects. To quantize this, we computed the expected counts from the
fitted $a$ in the same bins we used for the observed counts. That allowed us to
compute the poissonian probability in each bin, given by
\begin{center}
    $ \displaystyle p(k) = \frac{\l^k}{k!}e^{-\l}$
\end{center}
with $k$ the expected counts, $\l$ the observed counts. This work is done 100
times with a random number of total bins, $a$ being fitted 10 times on a
different and random number of bins used to fit each time. We interpolate these
1000 poissonian evolutions to get one final result that is as close as possible
to accurately represent how the probability to follow the expected rate evolves.

@@

\begin{table}[htbp!]
    \centering
    \caption{Number of SNe Ia effectively used for each survey, totalling 689
    Sne Ia. TO CORRECT FOR NEW ZMAX}
    \label{tab:sample}
    \begin{tabularx}{\linewidth}{|Y*{1}{|Y}|}\hline
        \rowcolor{gray!15} Survey & Number of SNe Ia \\\hline\hline
        SNf & 141 \\\hline
        PS1 & 178 \\\hline
        SDSS & 206 \\\hline
        SNLS & 138 \\\hline
        HST & 26 \\\hline
    \end{tabularx}
\end{table}

\begin{figure}[htbp!]
    \centering
    \subfigure[Method]{\label{fig:zdet}
        \includegraphics[width=\linewidth]{Article_figures/zmax_determination.pdf}}
    \subfigure[Result]{\label{fig:surveys_cuts}
    \includegraphics[width=\linewidth]{Article_figures/surveys_cuts_x.pdf}}
    \caption{(a) $z\St{max}$ determination from the interpolated poissonian
    evolutions; (b) SDSS, SNLS and PS1 samples cut at $z\St{max}$ as explained in
    section \ref{sec:sam}. The data we use is in plain markers.}
\end{figure}

\section{Method}

We used the LsSFR and stretch measurments from the SNf sample. The LsSFR has an
evolution with the redshift that is analytically known: calling $\de\z$ the
fraction of young stars and $\p\z$ the fraction of old ones, Rigault 2018 et +
find
\begin{equation}
    \frac{\de\z}{\p\z} \equiv LsSFR\z = K\times \LF{1+z}^\f
\end{equation}
with $\f = 2.8$, and knowing $\de\z + \p\z = 1$:
\begin{align}
    \de\z & = \LF{K^{-1}\times \LF{1+z}^{-\f} +1}^{-1}\\
    \p\z & = \LF{K\times \LF{1+z}^{+\f} + 1}\um
\end{align}

The goal is to find how the stretch depends on the LsSFR, distinguishing old and
young SNe which fractions evolve with the redshift, in order to have an
analytical law for the mean redshift evolution of the stretch. The measured data
on which we based our first model is plotted in figure \ref{fig:mod_first};
based of the shape of the $x_1$ vs LsSFR cloud, we implemented the following
model:
\begin{itemize}
    \item \textbf{young}: a gaussian of mean $\m_1$ and standard deviation
        $\s_1$, namely $\Nc_1 \equiv \Nc \LF{\m_1,\s_1}$;
    \item \textbf{old}: a linear combination between $\Nc_1$ and another
        gaussian $\Nc_2 \equiv \Nc \LF{\m_2,\s_2}$
\end{itemize}
As such, the probability to observe a young SNe Ia labeled "i" with a stretch
$x_1^i$ and error $\d x_1^i$ is
\begin{equation}
    p \LF{x_1^i, \d x_1{}^i|\m_1,\s_1} = \Nc \LF{\m_1, \Sq{\s_1{}^2 + \d
    x_1^i{}^2}}(x_1^i)
\end{equation}
and for an old one:
\begin{align}
    p(x_1^i, \d x_1^i | \m_{1,2}, \s_{1,2}, a) = a & \times \Nc \LF{\m_1,
    \sqrt{\s_1{}^2 + \d x_1^i{}^{2}}} (x_1^i) \ + \\ (1-a) & \times \Nc
    \LF{\m_2, \sqrt{ \s_2{}^2 + \d x_1^i{}^{2}}} (x_1^i), \nonumber 
\end{align}
We fit different model, and compare their AICc.

\begin{figure}[htbp!]
    \centering
    \subfigure[Raw data]{\label{fig:snf_data}
        \includegraphics[width=\linewidth]{Article_figures/BiGaussian_onlydata.pdf}}
    \subfigure[First implemented model]{\label{fig:3G2M2SSNF}
        \includegraphics[width=\linewidth]{Article_figures/BiGaussian.pdf}}
    \caption{Stretch des supernovae étudiées par la collaboration SNF en
    fonction de log(LsSFR). La couleur représente la probabilité pour une
supernova d'être issue d'un jeune progéniteur.}
    \label{fig:mod_first}
\end{figure}
